\subsection{Catering} 
Catering crews are yet another part of the ground handling crews. It is therefore interesting for this project to look into how their workday is structured.

When passengers are on long flights, there will be served meals for them, most of which consist of different kinds of meat, vegetables and drinks. The pilots are served with the same dishes, although this varies in between the different airlines\cite{cate_pilotfood1}\cite{cate_pilotfood2}. SAS offer breakfast when flying domestic flights, but only from 6 to 9 AM\cite{cate_SASIndri}. When flying in between Scandinavian and other European countries, there will always be served coffee or tea, but in order to get breakfast served the passenger has to be a member of premium service\cite{cate_SASscanda}.

All these air meals and drinks are prepared and made by the catering services, that are a part of the ground handling organization. The catering companies are chosen by the different airlines individually. SAS for example, have used Gate Gourmet\cite{cate_SASGourmet} as their catering service for a number of years. The catering services are very difficult in the sense of how complex the logistic aspect is, as the President of KLM Catering said "Flight catering is 70 
percent logistics and 30 percent cooking”\cite{cate_BookSection}. For this reason the catering services want their operations to go as smoothly as possible. The airline companies are also very interested in getting capable catering services, as they can then use the food as a marketing technique\cite{cate_BookSection}. 

Since logistics are so essential to the catering crews, a way to optimize their workday would be very beneficial for the catering companies, both by making the teams more efficient and by making the logistics aspect simpler.