\section{Airplane Mechanic}

The airplane mechanic has a very important job in the airport, their job is to repair the airplanes. It's therefore important that these working crews can acess the airplane that needs repairing quick and easy, and know where they needs to go, so the airplane can get flying again as quick as possible. It is also important that they does their job as good as possible, since they are responsible for safety of the plane, as every part needs to be maintained correctly.

In the north and the baltic countries, the leading airplain mechanic company regarding technical airplane maintenance is SAS Tech.\cite{sas_tech_mechanic}

If it would be possible for airplane mechanics to know excactely where to go by viewing it on a smartphone, PDA or other protable device, the mechanics would be able to be more productive, as they would know instantly where they where needed for their next task.

Boeing has released an app to help the mechanics get important things like airplane manuels, and serial numbers for specific parts. If they would be able to do this with every airplane, or every airplane at Aalborg Airport, it would help the mechanics tremendously as they would be able to identify the parts they needed much quicker, and therefore the maintenance of an airplane would be quicker. By using an app you would also be able to find earlier maintanence records, meaning that if another mechanic may have made a mistake, you would be able to identify it much quicker.\cite{cnet_boeing_app}

A downside to making an app like boing, could be the obvious problem of grease. If the Mechanics are supposed to use a tablet, PDA or smartphones, wouldn't they need to use a lot of time to clean their hands in between using the device, and would this really make the repairing of the aircraft faster?

Other suggestions for apps that could help mechanics do their job faster an better include:
\begin{itemize}
\item An app that gives suggestions how to fix things by describing the problem (Ex. Wierd Noise in Cabin)
\item An app that would help them calculate different thinsg, like what to set the torque screwdriver to. \ldots
\end{itemize}
