Some of the planning tools that is available to use:

% Overskrift Mind map
Mind map is a way to create a mental map of all the ideas that is important to a project.
Mind map does not require a huge knowlage of the desired project before creation.
The teknik is very simple, by putting the main topic in the middle, and then connecting all the valid thoughts to it.
Some of the bennefits that comes with mind map is, by creating an image of how the thoughts is connected, instead just plain text is, it's easier to pick up the thoughts processs from last work session.

% Overskrift SWOT analysis
SWOT is a abbreviation of Strengths, Weaknesses, Opportunities and Threats.
The method creates via a simple process, structure and overview over a organization strength and competitive position by focusing on the four above categories specified.

% Overskrift Gantt chart
A Gantt chart is a type of bar chart that illustrates a project schedule.
Gantt chart illustrating the dates of the start and end time of the tasks in the project and displays a summary of the project.

% Overskrift Scrum
Scrum is based on software development can be a complex and unpredictable process and therefore is more a form of controlled black box rather than a planned process.
This is one of the biggest differences between Scrum and waterfall and spiral methods that consider development as a fully orchestrated process.

Some of the benefits from Scrum are:
 - Flexible schedules
 - Flexible deadlines
 - Small development team
 - Frequent review
 - Object Orientation
 - Cooperation between development teams

